---
title: "Practical applications of brainmapr"
author: "Jean Fan"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

`brainmapr` visualizes 3D ISH gene expression data from the Allen Brain Atlas. Our goal is to spatially place a group of neuronal cells within a region of the brain based on their gene expression signature. This vignette recreates figures in [paper]

Load embryonic 13.5 day old mouse data. 

```{r}
library(brainmapr)
# Load data
load('../data-raw/RData/sids.RData')
load('../data-raw/RData/E13.5.energy.RData')
load('../data-raw/RData/E13.5.annot.RData')
```

Plot slice of whole mouse.

```{r, fig.show='hold'}
plot.projection.xray(vol3D, t=15)
s <- 26 # slice
s2 <- round(s/dim(gannot3D)[3]*dim(vol3D)[3]) # convert
plot.slice.xray(vol3D, s2, t=15)
```

Get forebrain.

```{r, fig.show='hold'}
# Plot x-ray of just brain component
# Forebrain
cids1 <- get.structure.ids(structure.id, 'forebrain')
cids2 <- get.structure.ids(structure.id, 'ventricles, forebrain')
cids <- c(cids1, cids2)
# Plot brain component; note section annotation data is for the left hemisphere only
sect3D <- structure.plot(cids, vol3D, annot3D, plot=F)
plot.projection.xray(vol3D, col=colorRampPalette(c("white", "grey"),space="Lab")(100), t=8)
plot.projection(sect3D, t=8, add=T)
plot.slice.xray(vol3D, s2, col=colorRampPalette(c("white", "grey"),space="Lab")(100), t=8)
plot.slice(sect3D, s2, t=8, add=T)
```

Gene expression signatures for proximal distal cell group identified by `pagoda`.

```{r, fig.show='hold'}
# Plot gene expression
# Upregulated genes
gl1  <- c("Dlx2", "Dlx6as1", "Sp9", "Pbx3", "Dlx5", "Dlx1", "Necap1", "Zfhx3", "Pou3f4", "Sec63", "Gdi1", "Rbp1", "Rbmx", "Nrxn3", "Map3k13", "Meis1", "Slc6a1", "Sp8", "Pbx1", "Dcx", "Gad2", "Sirt7", "Hmgcll1")
# lb * cZ
weights1 <- c(46.26915, 38.06011, 33.33369, 36.56755, 43.52929, 39.49066, 14.35763, 4.262908, 8.896505, 3.521533, 1.94611, 5.004284, 1.760767, 9.089976, 6.999584, 8.525134, 4.538585, 3.559675, 1.706482, 2.031702, 3.470824, 6.661706, 5.606481)
gp3D <- gene.plot(gl1, mat, gannot3D, plot=F, weights=weights1)
gpsect3D <- structure.plot(cids, gp3D, gannot3D, plot=F)
plot.projection.xray(vol3D, col=colorRampPalette(c("white", "grey"),space="Lab")(100), t=8)
plot.projection(gpsect3D, t=1, add=T)
plot.slice.xray(vol3D, s2, col=colorRampPalette(c("white", "grey"),space="Lab")(100), t=8)
plot.slice(gpsect3D, s, t=1, add=T)
# Downregulated genes
gl2 <- c("Celsr1", "Sp1", "Adck2", "Dkk3", "Bms1", "Eif2c3", "Bhlhe22", "Rcan2", "Tmem115", "Zfp654", "Smap1", "Map2k6", "Cadm4", "B4galt4", "Etl4", "Qsox2", "Hist1h1c", "1810041L15Rik", "Thap7", "Fuca1", "Stard4", "Rap1gds1", "Fam84b", "Pigh", "Ogfrl1", "Mdm1", "Syde2", "Gm166", "Ccdc171", "BC023829", "9230110C19Rik",
         "Lin9", "Clpp", "Xrcc4", "Vrk3", "Cdk5rap1", "Lrr1", "Spty2d1", "Ext2", "Tex261", "1810044D09Rik", "Gpr156", "2410127L17Rik", "Pdp2", "E2f8", "Tenm4", "D3Ertd751e", "Prtg", "Mrps26", "Rabac1", "Chaf1b", "Gm17762", "Trim3", "Cpeb2", "Rmi1", "Klf16", "Echdc1", "Hdac7", "Gadd45a", "Myo7a", "Safb2", "Scml2", "Pbk",
         "Slc16a1", "Atp2b1", "Polr3h", "Mlst8", "Cradd", "Avl9", "Ndc80", "Ift74", "Eomes", "Slit2", "Phf13", "Oscp1", "Cd9", "Nufip1", "Sft2d2", "Col18a1", "Mipep", "Lamb1", "Rrp15", "Rfxap", "Neurod2", "Melk", "Wdr35", "Fam53b", "Faim", "Ankib1", "Pim3", "Tcn2", "Sptlc1", "Lmf1", "2700050L05Rik", "P4ha1", "Ugdh",
         "2510003E04Rik", "Unc50", "Trappc6a", "Urm1", "Ccdc117", "Zdhhc24", "Osbpl5", "Spg20", "Prrc1", "Sh3pxd2a", "Tef", "Cbln2", "AI414108", "Znrf3", "Phlpp2", "Mpp6", "Dhx33", "Spg21", "Ankrd40", "Smyd5", "Fbln1", "Sapcd2", "Rnft1", "Nfix", "Wee1", "Vkorc1l1", "Zfp574", "Nap1l2", "Dusp14", "Ccdc112", "Epb4.1l2",
         "1810055G02Rik", "Kctd3", "Hap1", "Ccdc40", "Wdr3", "Synpr", "Arhgap31", "Zc3h7a", "Cenph", "Gpank1", "Kdm2a", "Smad3", "1190002N15Rik", "Ptar1", "Klf6", "Lpar4", "Uaca", "Stk24", "Tmem248", "Lipt1", "Hmga2", "Rnf26", "Asb1", "Add3", "Ankzf1", "Fbxo25", "Zfp955b", "Fbxl6", "Bcl2l12", "Cystm1", "Thop1", "Trmt13",
         "Tmem179b", "Slu7", "Nucb1", "Scd1", "Nptx1", "Ppap2c", "Pcdh18", "Nrxn1", "Lap3", "Asb3", "Ano1", "Arhgef25", "Acad8", "Pgap2", "Fam179b", "Tceb3", "Tnik", "Dap3", "Slc25a24", "E2f6", "Sox3", "Cyth3", "Tspan12", "1700102H20Rik", "Dgkd", "Maml1", "Fgfr2", "Klhdc4", "Incenp", "Vcam1", "Atl3", "Rai2", "Tm7sf2", "Napepld",
         "Fert2", "Cldn12", "Itpr1", "Katnb1", "Hyal2", "Gys1", "Mcu", "Pacrgl", "Aldoc", "Lhpp", "Pi4k2b", "Rem2", "Polr3a", "Ptpn13", "2310039H08Rik", "Col11a1", "Dph2", "Ddrgk1", "Tmem101", "Gas2", "Cdc45", "Tmem126b", "Pofut2", "Cep68", "Npc1", "Lpar1", "Adamts20", "Bcl10", "Mir135a-2", "Snap23", "Sesn1", "Pde3b", "Slk", "Dennd1b",
         "Plk1s1", "Trak1", "Galnt7", "E2f7", "Rpia", "2010204K13Rik", "Mbd1", "Tmem178", "Gmds", "2010107G23Rik", "Rab30", "Zbed3", "Coasy", "Fntb", "Wnt8b", "Ndn", "Rspo3", "Dnajb12", "Map4k3", "Caml", "Tceal1", "Cdpf1", "C1galt1c1", "Smap2", "Ece2", "Pvrl2", "Noc4l", "Trps1", "Nubpl", "Fgfbp3", "Pold1", "Sil1", "Zmym1", "2310035C23Rik",
         "Cluh", "Rexo2", "Frrs1l", "Sstr2", "Herc3", "Slc25a36", "Fahd1", "Fam196a", "Alcam", "Atrip", "Smpd2", "Hdgfrp2", "Tanc1", "Pspc1", "Gusb", "Dgcr6", "Slc30a10", "Flrt2", "Gdap2", "Zfp770", "Tmem110", "Prr15", "Hsd17b7", "Per3", "Tiparp", "Gcat", "AW554918", "Ogfr", "Gne", "Ap4m1", "Mlf1", "Ppp4r2", "Pms1", "Tmed5", "Mtg1",
         "Fars2", "Dbndd1", "Tmem251", "Cdk2ap2", "Dennd1a", "Prdm5", "Ercc3", "Fam169a", "Vps52", "Nynrin", "1700020I14Rik", "Athl1", "Asrgl1", "2700099C18Rik", "Obfc1", "Necab3", "Adnp2", "Nckap5", "Ptgr1", "Ptpmt1", "Zscan22", "Msto1", "Sdc4", "Rgcc", "Vkorc1", "Hist1h4i", "Tmem14a", "Wfdc2", "Baiap2l1", "Gemin6", "D330022K07Rik",
         "C430049B03Rik", "Slc35b2", "Ext1", "Brca1", "Rnf11", "Zbtb17", "Dtd2", "Sap30l", "Akip1", "Zfp449", "Mpp5", "Kbtbd11", "Zmym3", "Tmed3", "2700097O09Rik", "Slc9a1", "2810408I11Rik", "Nup43", "Zfp276", "Gm15545", "Zfyve16", "Rcn3", "Ccrn4l", "Ift172", "Pgs1", "Rwdd3", "Mettl23", "Chrna3", "Ttc8", "Ndufaf1", "Zfp719", "Bre",
         "Dpm1", "Gm11627", "Exoc6b", "Eme1", "Ccdc138", "Hunk", "Wdr60", "Fam173b", "Cntn5", "Grtp1", "Nedd9", "Gtf2h4", "Tfap2c", "Fut9", "Osbpl11", "0610007N19Rik", "Fndc3c1", "Slc17a7", "Prosc", "Ngly1", "Nme3", "Neurod1", "Pcp4", "Cdk19", "Coq4", "Smim8", "Elmod3", "Cad", "2810002D19Rik", "Sc5d", "BC030867", "Gpc3", "Pafah2", "Hadhb",
         "Usp25", "Itm2a", "Plekhf2", "Pef1", "Pcsk6", "Dach2", "Sat1", "Prokr1", "Zkscan17", "Pold3", "Nkrf", "Mmd2", "Alad", "Enpp5", "Man1b1", "Traf3ip1", "Fut10", "Ptplb", "Dnajb2", "BC022687", "Ift122", "Jph1", "1110012L19Rik", "Cdk5rap2", "Dym", "Abhd6", "A330048O09Rik", "Nop14", "Gm9958", "Zufsp", "Emx1", "Qtrt1", "Lman1", "Ppp1r14a",
         "Stx8", "Adck5", "Tmem216", "Plxna4", "Pdha1", "Appl2", "Coil", "Slc17a6", "Hs3st1", "Slc35a2", "Zfp36l2", "Atxn1l", "Blvra", "Cables2", "Ttpal", "2210016L21Rik", "Lrrc57", "Aspscr1", "Spice1", "Lmcd1", "Bora", "Ddx28", "Gemin2", "Gba", "Ralb", "Cdt1", "Prelid2", "Hey1", "5330426P16Rik", "A730017C20Rik", "Cntrob", "Bivm", "Rtn2", "Neurod6",
         "Sh3gl1", "Phldb2", "Galnt14", "Pgm1", "Esco2", "Msl3", "Cbln4", "Zfp763", "Mecr", "Gpr89", "Lsm10", "Coq9", "Akap10", "Shmt2", "Nhlh1", "Ubox5", "Lrrn1", "Cep57l1", "Adamts10", "Mterfd3", "Prim2", "Tnfaip8", "Gpr19", "Masp1", "Jag1", "Enoph1", "Mgme1", "Suclg2", "Pinx1", "Ube2t", "Arl6", "Cers2", "2810055G20Rik", "Tmem132c", "Atic", "Actr1b",
         "Asah1", "Nfia", "Rprd1a", "Neurog2", "0610031J06Rik", "Otx1", "Litaf", "Nr2e1", "Plp2", "Ankrd13c", "Uchl5", "Taf12", "Serpini1", "Gja1", "Nfib")
weights2 <- c(13.61864, 14.61415, 12.08321, 10.71039, 14.41029, 9.096843, 11.57122, 11.90863, 11.66958, 12.82011, 12.98447, 15.12115, 9.209305, 12.82725, 14.80067, 13.23838, 10.12313,
              14.07884, 14.08529, 11.53182, 13.09685, 14.08529, 13.67344, 11.37786, 11.37786, 13.36228, 10.41103, 10.10093, 9.606883, 14.74488, 12.03396, 14.68973, 17.09652, 12.03396,
              13.61946, 10.7984, 9.151281, 10.74603, 11.32915, 10.91604, 12.0034, 11.02835, 14.56363, 12.7291, 10.22225, 13.8366, 11.24725, 11.08771, 10.24773, 12.09757, 15.28999, 10.66939,
              14.44988, 12.52891, 12.5483, 10.69896, 10.69896, 13.22628, 12.72598, 11.37924, 13.32341, 10.625, 16.38446, 13.25959, 15.63164, 14.19521, 9.473503, 11.76694, 14.00611, 14.95135,
              17.24502, 13.84699, 14.8664, 10.87371, 10.61886, 13.59214, 12.99748, 14.78145, 10.87371, 14.44556, 10.53676, 14.53523, 10.9089, 14.74563, 14.8464, 12.45732, 12.71329, 14.8464,
              14.5051, 12.0307, 10.06825, 11.00681, 11.34999, 12.69911, 13.39316, 14.34291, 10.73571, 13.82759, 10.05256, 14.38757, 15.73909, 12.62815, 11.59022, 12.63262, 11.59432,
              11.8539, 10.72908, 13.93049, 11.42467, 13.07825, 14.91031, 13.26324, 12.16026, 14.10128, 10.88062, 11.75469, 15.06536, 14.71703, 11.49496, 13.49787, 14.8912, 10.79829,
              14.10745, 11.32921, 15.51246, 11.24218, 12.98575, 15.34549, 13.34012, 10.12108, 12.9131, 11.95335, 12.3896, 11.95335, 14.57087, 10.81909, 16.05413, 14.13461, 12.5641, 13.61111,
              11.27084, 12.58141, 12.66878, 11.62033, 10.59083, 16.45585, 11.46658, 18.81919, 15.06599, 15.50395, 15.59154, 11.33856, 15.55755, 10.54749, 15.20597, 13.71174, 11.35899, 14.2745,
              13.12901, 15.60724, 15.95995, 15.25453, 14.55213, 11.90629, 11.37712, 14.99311, 13.67019, 16.31603, 16.66881, 12.52365, 14.58196, 12.37257, 12.04586, 15.4319, 16.05273, 14.74214,
              16.69591, 11.63385, 15.54141, 13.76525, 15.18618, 16.25187, 10.21293, 14.3869, 11.36743, 15.63022, 16.16498, 15.89852, 16.34262, 10.6738, 10.8517, 11.38539, 12.45277, 15.56597,
              10.76802, 12.99281, 16.28551, 16.10753, 11.65793, 13.00968, 14.61361, 13.3661, 15.41557, 10.79827, 10.97676, 14.45719, 12.85084, 15.9743, 16.15279, 15.90458, 16.08463, 14.26838,
              15.88367, 15.43498, 13.28126, 11.4865, 15.52472, 12.56336, 15.16577, 13.99917, 15.88367, 11.66597, 13.01205, 15.16577, 14.09358, 14.9015, 15.44011, 12.49463, 13.75309, 15.64076,
              15.47179, 11.78375, 11.78375, 12.95313, 15.6517, 15.74165, 14.84213, 14.67065, 14.77473, 12.79275, 16.39635, 13.60356, 14.51291, 16.76647, 10.36636, 14.96362, 16.58618, 12.64003,
              16.25147, 10.9246, 11.5566, 15.89032, 15.80004, 15.07775, 13.81375, 14.89718, 12.91089, 14.17489, 11.46631, 15.25832, 15.16804, 11.5566, 15.25832, 16.16118, 15.43889, 11.01488,
              12.1886, 11.91774, 16.07089, 13.63317, 15.80004, 13.90403, 13.99432, 12.36917, 15.43889, 12.8206, 16.61261, 15.25832, 15.98061, 15.07775, 15.07775, 11.82746, 9.841166, 13.00117,
              14.26518, 16.25147, 16.25147, 14.44575, 14.71661, 15.98061, 12.73032, 16.43204, 16.07556, 15.98636, 12.92251, 15.96586, 16.05658, 9.986869, 16.09098, 16.54553, 13.5527, 11.73354,
              15.64746, 15.37637, 15.31162, 16.45403, 16.09669, 15.46323, 15.82922, 11.71179, 16.80268, 16.34359, 16.43541, 15.60905, 12.76269, 13.40542, 10.65088, 16.52723, 14.23178, 16.34359,
              16.73998, 16.38034, 16.22932, 16.69038, 11.06544, 16.79128, 10.42703, 12.75515, 14.32643, 14.97343, 15.80529, 15.89772, 15.71286, 14.60372, 10.64724, 13.98703, 15.56888, 15.75423,
              13.99346, 12.78873, 17.05163, 16.95896, 16.31026, 14.08613, 17.05163, 11.12063, 11.02796, 16.58827, 16.86629, 16.21759, 11.86201, 15.93957, 17.42232, 17.42232, 15.10552, 17.05163,
              13.80812, 11.86201, 16.77362, 17.60767, 12.60338, 15.8469, 14.54949, 11.58399, 14.73484, 16.77362, 13.06674, 12.04735, 12.04735, 16.40293, 16.58827, 17.05163, 16.86629, 14.92018,
              15.47621, 16.86629, 10.65727, 14.08613, 12.78873, 16.77362, 18.07102, 15.47621, 12.14002, 16.31026, 16.31026, 11.58399, 13.90079, 16.4956, 15.93957, 15.29087, 15.66155, 12.51071,
              16.86629, 12.60338, 17.32965, 15.01285, 15.10552, 12.14002, 13.06674, 15.93957, 15.01285, 16.40293, 16.58827, 12.69605, 17.14431, 16.77362, 12.32537, 15.10552, 14.36415, 12.51071,
              14.73484, 14.27148, 16.95896, 12.60338, 15.75423, 17.23698, 13.5301, 15.75423, 14.64216, 16.40293, 15.8469, 11.67666, 16.68095, 16.68095, 16.21759, 15.93957, 13.25208, 17.14431,
              12.97407, 16.95896, 16.12491, 17.23698, 12.78873, 13.80812, 17.23698, 17.42232, 14.36415, 16.4956, 15.56888, 13.06674, 16.21759, 16.31026, 13.43743, 16.86629, 12.69605, 15.66155,
              15.47621, 16.21759, 16.40293, 17.05163, 14.82751, 13.43743, 13.06674, 15.47621, 15.01285, 16.12491, 16.31026, 13.06674, 16.12491, 16.4956, 17.51499, 17.14431, 16.12491, 14.64216,
              15.66155, 15.66155, 15.8469, 13.43743, 16.03224, 16.77362, 16.31026, 17.70034, 16.58827, 15.01285, 16.77362, 16.77362, 16.4956, 17.14431, 16.4956, 16.12491, 17.14431, 15.47621,
              13.99346, 16.12491, 14.36415, 15.01285, 13.80812, 16.68095, 15.56888, 16.86629, 16.77362, 17.60767, 17.42232, 17.51499, 17.42232, 17.60767, 16.77362, 17.51499, 11.2133, 16.68095,
              17.14431, 16.86629, 14.64216, 16.95896, 15.56888, 17.60767, 16.77362, 17.23698, 17.70034, 19.3685, 18.97918, 61.6922)
gp3D <- gene.plot(gl2, mat, gannot3D, plot=F, weights=weights2)
gpsect3D <- structure.plot(cids, gp3D, gannot3D, plot=F)
plot.projection.xray(vol3D, col=colorRampPalette(c("white", "grey"),space="Lab")(100), t=8)
plot.projection(gpsect3D, t=1, add=T)
plot.slice.xray(vol3D, s2, col=colorRampPalette(c("white", "grey"),space="Lab")(100), t=8)
plot.slice(gpsect3D, s, t=1, add=T)
```

Compare relative placement.

```{r, fig.show='hold'}
gp3D <- gene.plot.weighted.comp(gl1, weights1, gl2, weights2, mat, gannot3D, plot=F)
gpsect3D <- structure.plot(cids, gp3D, gannot3D, plot=F)
plot.slice.xray(vol3D, s2, col=colorRampPalette(c("white", "grey"),space="Lab")(100), t=8)
plot.slice.comp(gpsect3D, s, add=T)
```

Gene expression signatures for top subpopulation split in neuroprogenitor cells identified by `pagoda`.

```{r, fig.show='hold'}
gl1 <- c("Kif23", "Rad51", "Pole", "Mcm10", "Pabpc4l", "Pola1", "Ifi30", "Tmem97", "Cdc6", "Cdca5", "Gins2", "Prdx1", "Ticrr", "Car14", "Mis18bp1", "Kntc1", "Cdc45", "Wee1", "Poc1a", "Mgme1", "Ncaph", "Exo1", "Isyna1", "Rad54b", "Shmt1", "Sgol1", "Shcbp1", "Vcam1", "Bora", "Hmgb2", "Cenpn", "Esco2", "Espl1", "Pole2", "BC030867", "Zfp367", "Sox3", "Pus3", "Ndc80", "Pold1", "2810408I11Rik", "Lpar1", "Lhfpl2", "Ccnf", "Gpx7", "BC055324", "Megf10", "Fgfbp3", "Cdt1", "2700099C18Rik", "Arhgef39", "Suv39h2", "Trps1", "Clspn", "Siva1", "Gulp1", "Setdb2", "Rpa2", "Wwtr1", "Ak4", "Ing5", "Crip1", "Orc1", "Acrbp", "Arhgap31", "Rad50", "Rragb", "Med26", "Samhd1", "Lpcat1", "Dhx32", "Mms22l", "B330016D10Rik", "Clu", "Gm11627", "Dctd", "Dleu2", "Atad5", "Fgfr2", "Pxdn", "H2afz", "Ran", "Tyms", "Kbtbd11", "Hist1h1b", "Ercc6l", "Syde2", "D3Ertd751e", "2810417H13Rik", "Scml2", "Kif2c", "Kif22", "Depdc1a", "Tmem98", "Tyro3", "Ccdc77", "Adat1", "Tk1", "Sfxn5", "BC052040", "Mybl2", "Sox2", "Gm3893", "Ptpru", "Fn1", "Npm1", "Mad2l1", "Fbxo30", "Etl4", "Rpsa", "Aif1l", "Hmgn2", "Lrrc1", "Cad", "Hes1", "Hmgb1", "Msrb2", "Ogfod3", "Cluh", "Hells", "Diap3", "Gapdh", "Cenph", "Kif14", "Thoc3", "Dusp16", "Rev1", "9430015G10Rik", "Traf3", "Exosc8", "Rad51ap1", "Cdk2", "Ppic", "Neil3", "Tom1l1", "Prr14", "Xpo4", "Tgfb2", "Arhgap17", "Igflr1", "Gpx8", "Paics", "Hirip3", "Gen1", "Polq", "Fbxo5", "Uck1", "Tcf7l2", "Mipep", "Dnaaf2", "0610007N19Rik", "Actn1", "Atp5sl", "Pla2g12a", "Cdca7", "Scd1", "Tuba1b", "2610015P09Rik", "Mir3112", "Gtse1", "Nedd9", "Cry1", "Nasp", "Exosc7", "Iqcc", "Tmem110", "Acot1", "Grb10", "S1pr1", "Ckap2", "Coq10a", "Idi1", "Cdca7l", "Incenp", "Mettl16", "Mdk", "Haus5", "Cks1b", "Tmed5", "Pdpn", "Gpc3", "Gar1", "Igsf11", "Msh6", "Mif", "Zfp36l1", "Igfbp5", "Mns1", "Dgkd", "Sdc1", "Zfp748", "Kazn", "Prr15", "Top2a", "Etaa1", "Sapcd2", "Notch2", "Agpat3", "Gatad2a", "Nde1", "Dnajc3", "Gmds", "Psat1", "Fras1", "Cenpm", "Casc5", "Adamts6", "Zadh2", "Mt1", "Zfp579", "Mki67", "Set", "Sfrp2", "4930422G04Rik", "Zfyve21", "Ddx51", "Gas1", "Haus3", "Ect2", "Fam84b", "Cenpp", "Rlbp1", "Nmral1", "Hist1h4i", "Bmpr1b", "Chtf18", "Metrn", "Nrde2", "Lrr1", "Mir17hg", "Hspd1", "Sav1", "Fzd10", "Fndc3c1", "Slbp", "4931417G12Rik", "Hn1l", "Six5", "Enoph1", "Ccnd2", "Kif4", "Gorab", "1190002F15Rik", "Gins1", "Wnt5b", "Snap23", "Cln3", "Gm8096", "Cpped1", "Jmy", "Fam229b", "Ajuba", "Stard4")
weights1 <- c(25.70137, 29.59888, 29.76567, 24.68016, 20.78329, 30.52546, 12.57898, 23.69041, 24.49737, 21.06707, 32.37425, 5.917703, 19.79369, 21.01805, 25.45902, 22.69036, 23.80137, 21.25906, 16.99061, 18.17822, 17.96696, 17.36431, 17.05992, 14.48438, 21.92231, 19.96471, 17.36249, 19.89858, 15.78619, 6.346554, 17.87554, 20.61649, 5.917697, 19.22824, 16.48714, 22.7253, 13.72571, 13.32367, 19.62173, 16.07113, 15.13676, 21.24849, 14.2775, 16.07539, 14.12963, 11.73834, 15.93613, 10.93345, 11.10596, 9.628688, 9.79836, 16.14695, 14.06795, 23.8073, 7.214335, 10.8215, 11.636, 20.89295, 8.902458, 7.897001, 17.6958, 6.402814, 9.927401, 9.585663, 8.215373, 15.92776, 8.194774, 6.135632, 10.93828, 7.952126, 16.78108, 16.1418, 2.070826, 6.528858, 9.800817, 11.02213, 9.256968, 16.95434, 12.59132, 8.249959, 2.740084, 2.878239, 4.189773, 14.78767, 18.76207, 1.33938, 5.344057, 6.081742, 6.228143, 3.545454, 9.881127, 20.20164, 3.719686, 12.51794, 11.40345, 12.55717, 7.988526, 16.67645, 8.497081, 5.096289, 2.680227, 16.3119, 3.742364, 5.846637, 17.05004, 1.718221, 10.56812, 9.421022, 14.12226, 1.699372, 17.3678, 2.077661, 0.6450837, 12.12757, 12.55257, 1.53705, 10.15608, 2.53861, 8.247943, 12.41625, 1.642412, 1.629888, 5.639646, 3.234741, 12.14668, 4.45925, 9.412865, 5.930603, 7.660363, 3.666648, 2.547089, 11.78479, 12.261, 2.025131, 4.379496, 11.31754, 1.280813, 2.444286, 5.080282, 1.151702, 4.837149, 1.957394, 10.35392, 1.138974, 1.366205, 12.28883, 1.020337, 13.09234, 6.433306, 6.510424, 9.765636, 10.70904, 1.219111, 7.532179, 5.637852, 5.4065, 1.321662, 8.798219, 1.094809, 1.092081, 0.9728729, 0.9702798, 2.048368, 2.667087, 5.972456, 3.175221, 0.2115612, 2.327173, 0.2101568, 5.848486, 0.8351951, 2.916965, 3.436796, 9.419663, 8.348403, 1.2368, 8.347702, 1.748644, 8.086359, 8.802871, 8.393264, 6.835873, 3.0586, 10.96285, 1.116587, 4.741809, 7.759272, 7.842224, 7.012087, 6.010361, 4.607943, 5.191336, 3.076776, 3.572298, 1.765293, 0.7824073, 7.956223, 7.234441, 2.122103, 5.009876, 6.250351, 0.7641022, 2.843459, 0.7556067, 6.598702, 8.607848, 4.863156, 0.09266894, 6.300077, 0.8268156, 3.471054, 0.8220918, 4.737982, 8.173211, 4.712872, 0.09035995, 5.151065, 4.966644, 5.934447, 3.802551, 7.073224, 0.4405537, 1.760735, 6.330614, 6.589453, 7.280396, 0.8713346, 5.207967, 0.4322329, 4.748665, 1.033637, 0.8578934, 0.08547415, 7.000531, 1.535777, 0.0850716, 4.053823, 0.4203083, 6.716998, 0.9235872, 6.528929, 5.439931, 3.548127, 5.280641, 0.3300401, 2.31028, 4.680702, 0.08206534, 3.604325, 6.05617, 4.008056, 3.190085, 0.6513329)
gp3D <- gene.plot(gl1, mat, gannot3D, plot=F, weights=weights1)
gpsect3D <- structure.plot(cids, gp3D, gannot3D, plot=F)
plot.projection.xray(vol3D, col=colorRampPalette(c("white", "grey"),space="Lab")(100), t=8)
plot.projection(gpsect3D, t=1, add=T)
plot.slice.xray(vol3D, s2, col=colorRampPalette(c("white", "grey"),space="Lab")(100), t=8)
plot.slice(gpsect3D, s, t=1, add=T)
# Top split group 2
gl2 <- c("Ftl1", "Stmn3", "Rnf185", "Serinc5", "Plk3", "Nfasc", "Apc", "Khdrbs2", "1810041L15Rik", "Celsr3", "Klhdc5", "Plch2", "Tram1l1", "Plcl1", "Calcoco1", "Gm2694", "2510009E07Rik", "Srgap1", "Klf7", "Nhlh2", "Nsg2", "Tmtc4", "Nkain3", "Actr2", "Wdr83", "Ina", "Celf3", "Pak7", "Slc4a8", "Gpr19", "Fam5b", "Gpr137", "Atp6v1g1", "Shisa7", "Neurod1", "Slc35a1", "Nme3", "Fkbpl", "Apc2", "Frmd4b", "Clvs1", "Evl", "Dcc", "Kif3c", "Ank", "Mbnl2", "Tubb4a", "Brwd3", "Cacna2d1", "Sgip1", "Itm2b", "Ccser1", "Ndfip2", "Klhl29", "Yod1", "Vcan", "Ppm1a", "Hn1", "Atl1", "Fam84a", "Atp6v1f", "Atg16l1", "Rbfox1", "Pcnxl4", "Jakmip2", "Rab3d", "Stxbp1", "Tspyl4", "St8sia3", "Mon2", "Shank1", "Cabp1", "Slc27a4", "Ptprs", "Jup", "Pcdh7", "Rfx3", "Ankzf1", "Kdm6b", "Hist3h2a", "Gramd1a", "Cdk14", "Lcor", "Elavl4", "Slco5a1", "Tmem44", "Cntfr", "Ikbkb", "Ptpro", "Mfap4", "Ankrd12", "Trim46", "Atp6v1e1", "Pcp4", "Gcdh", "Necab3", "Cpeb4", "Rab3a", "Nuak1", "9330133O14Rik", "Frmd5", "Frrs1l", "Rcan2", "Prdm8", "Selk", "Cdyl2", "Dhtkd1", "Kcnq2", "Vps37c", "Actg1", "Gas8", "Rwdd3", "Sema6d", "Ypel5", "Cttnbp2", "Islr2", "Neurod6", "Cbln2", "Ncan", "Fam57b", "Atg9a", "Ppp1r14a", "Cdk5r1", "Kalrn", "Snap91", "Tanc2", "Crmp1", "Edil3", "Kif5a", "Ralgps1", "Disp2", "Ass1", "Tmsb4x", "Dbc1", "Mapre3", "Zzef1", "Gna12", "Gstm7", "Sv2b", "Tiam2", "Zfp46", "Ank3", "Calm2", "Nrn1", "Jph4", "Snap25", "Ttc3", "Oscp1", "Cntn2", "Fam49a", "Serpini1", "Rab3c", "Chst15", "Sv2a", "Dpysl3", "Sema4g", "Elavl3", "Vps13c", "Scn3a", "Nav3", "Cnr1", "Atp2b2", "Nnat", "Rufy3", "Tmsb10", "Nefm", "Tnfrsf21", "Kif21b", "Mcf2l", "Stmn1", "Gmnc", "Hecw1", "Enpp5", "L1cam", "Sorbs2", "Cdc42ep2", "Nmnat2", "Tuba1a", "Unc79", "Scn3b", "3632451O06Rik", "Pde1c", "Lrfn5", "Rtn2", "Gabrb2", "Slc17a6", "1700088E04Rik", "Trappc6a", "Psd", "Hmgcll1", "Nav1", "Tub", "Actl6b", "March8", "Pxk", "Tbr1", "Lrrc7", "Akap6", "Dscaml1", "Dnajc6", "Dopey2", "Galnt14", "Osbpl5", "Mllt11", "Sez6l2", "Nxph4", "Gabrg2", "Tubb3", "Chga", "Gdi1", "Dusp8", "Cd200", "Nrxn1", "Ralyl", "Mapk10", "Sox11", "Wnt7b", "Ndrg4", "Magel2", "Cbln4", "Dner", "Myt1l", "Dusp4", "Map2", "Syt4", "Atp1a3", "Smim18", "Ppfia2", "Plxna4", "Rtn1", "Map1b", "Snrpn", "Nrep", "Dcx", "Stmn2", "Tagln3")
weights2 <- c(2.136911, 9.205157, 15.04057, 14.38306, 15.63322, 15.21329, 7.556623, 15.73863, 15.24225, 14.90353, 16.34308, 4.423723, 16.73704, 12.81987, 15.2705, 16.21419, 14.84824, 15.80225, 15.23299, 14.40521, 9.90502, 16.11969, 12.89575, 3.311071, 17.46972, 18.18689, 15.31839, 16.47549, 15.68371, 16.4865, 12.65875, 15.94118, 3.6415, 15.56466, 18.86522, 17.09324, 17.45138, 17.43719, 14.81852, 16.76695, 16.04711, 16.71587, 8.95732, 15.21574, 16.57723, 17.9463, 18.28922, 17.0956, 18.51236, 14.47279, 8.607997, 16.33777, 17.69629, 18.0779, 18.39833, 8.384968, 17.93645, 3.883598, 18.37481, 19.62326, 7.079478, 18.46066, 18.57387, 19.86684, 17.57067, 17.17134, 19.19559, 17.28012, 19.51456, 18.63038, 16.346, 11.30094, 11.65711, 3.8573, 18.27631, 19.3324, 10.47136, 19.1688, 7.534274, 12.81903, 16.9127, 17.81924, 17.61544, 10.82315, 20.32141, 19.71257, 18.33481, 19.41048, 18.02951, 20.99936, 20.16026, 18.26461, 9.186602, 21.50746, 16.10645, 22.00737, 8.978131, 21.77559, 21.36687, 20.04521, 19.50468, 21.11922, 18.66986, 17.83665, 5.94918, 16.38831, 13.5438, 18.87614, 20.60921, 4.189785, 22.75836, 23.09122, 17.50587, 11.29154, 22.14349, 22.18913, 27.94501, 22.19199, 9.658578, 21.14181, 21.52989, 21.78602, 23.19786, 24.72262, 24.1665, 20.88067, 16.71132, 24.0294, 23.02293, 20.88419, 15.83706, 16.24816, 6.450837, 23.94848, 23.94848, 25.70524, 19.99748, 26.62003, 22.178, 24.94079, 24.08407, 26.47341, 6.700568, 28.2764, 22.20154, 25.95458, 6.91906, 25.88305, 22.42306, 27.05859, 30.87535, 21.7612, 22.35798, 25.03427, 17.46535, 27.2852, 16.16853, 27.74718, 31.36692, 28.40496, 35.20579, 30.09073, 8.811513, 18.08419, 7.209913, 25.47581, 25.36688, 31.83581, 28.58641, 6.66765, 30.0685, 31.42778, 30.04373, 29.97091, 27.10214, 30.83477, 25.14173, 8.179623, 29.54644, 30.6819, 31.9696, 31.49879, 31.99548, 33.65421, 32.11973, 37.97322, 24.91364, 31.93946, 30.68069, 33.96646, 30.45905, 34.63189, 34.76243, 35.00472, 35.09193, 39.13838, 33.9888, 37.8095, 35.00221, 32.88669, 35.75556, 38.66944, 36.92484, 21.31074, 38.37572, 35.98967, 31.81786, 30.92585, 30.85406, 22.2424, 39.26337, 40.44131, 41.71698, 39.48613, 38.26427, 14.63608, 40.31382, 40.53405, 42.45989, 43.87076, 43.02692, 45.8313, 41.15421, 27.19848, 48.42665, 45.21538, 48.54704, 48.93636, 47.4931, 33.36695, 19.00539, 46.4681, 31.47316, 56.75082, 60.46812, 28.49932)
gp3D <- gene.plot(gl2, mat, gannot3D, plot=F, weights=weights2)
gpsect3D <- structure.plot(cids, gp3D, gannot3D, plot=F)
plot.projection.xray(vol3D, col=colorRampPalette(c("white", "grey"),space="Lab")(100), t=8)
plot.projection(gpsect3D, t=1, add=T)
plot.slice.xray(vol3D, s2, col=colorRampPalette(c("white", "grey"),space="Lab")(100), t=8)
plot.slice(gpsect3D, s, t=1, add=T)
# Comparison
gp3D <- gene.plot.weighted.comp(gl1, weights1, gl2, weights2, mat, gannot3D, plot=F)
gpsect3D <- structure.plot(cids, gp3D, gannot3D, plot=F)
plot.slice.xray(vol3D, s2, col=colorRampPalette(c("white", "grey"),space="Lab")(100), t=8)
plot.slice.comp(gpsect3D, s, add=T)
```
